---
output: github_document
link-citations: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(roundwork)
```

# roundwork

<!-- badges: start -->

[![R-CMD-check](https://github.com/lhdjung/roundwork/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lhdjung/roundwork/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The goal of roundwork is to enable flexible rounding beyond `base::round()`. Its main API is `reround()`, from which all implemented rounding procedures can be accessed. This is useful to reconstruct how others may have rounded their data.

Given a rounded number, call `unround()` to get the lower and upper bounds of the original number. This also takes rounding options into account, just like `reround()` does.

Many roundwork functions used to be part of [scrutiny](https://lhdjung.github.io/scrutiny/). They were outsourced here for better modularity within the errorverse.

## Installation

You can install the development version of roundwork like so:

``` r
remotes::install_github("lhdjung/roundwork")
```

## Get started

Round in some specific way, e.g., up from 5:

```{r}
round_up(4.1679, digits = 2)
```

Use `reround()` to round more flexibly, especially in your own functions. You can specify a rounding procedure:

```{r}
reround(4.1679, digits = 2, rounding = "up")
```

Ceil or floor numbers if certain strong assumptions are permitted:

```{r}
reround(4.1679, digits = 2, rounding = "floor")
```

The default is to return two numbers — one rounded up, one rounded down. This is best for conservative assumptions, so that your conclusions won't hinge on edge cases where these rounding procedures differ.

```{r}
reround(1.275, digits = 2)
```

### Bounds on the unrounded number

`unround()` computes the range of an unknown original number, given its rounded version. The rounding procedure determines whether the bounds are inclusive or not:

```{r}
unround("3.60")

unround("3.60", rounding = "up")

unround("3.60", rounding = "even")
```
