---
title: "Relation to scrutiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Relation to scrutiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The roundwork package was outsourced from [scrutiny](https://lhdjung.github.io/scrutiny/), a much larger and less focused package. (See [this Github issue](https://github.com/ianhussey/ERROR/issues/6) for the rationale.) However, all functions that were copied to roundwork are still part of scrutiny as of version 0.5.0.

For now, this can create ambiguities when using both packages together. Here is how to avoid such problems in an interactive script. Package developers should simply use `package::function()` syntax, as usual.

## Resolving conflicts

Make sure that all roundwork functions are used instead of their scrutiny counterparts by the same names. To do so, use the [conflicted](https://conflicted.r-lib.org/index.html) package:

```{r eval=FALSE, include=FALSE}
library(conflicted)
library(scrutiny)
library(roundwork)
conflict_prefer_matching("round", "roundwork", quiet = TRUE)
```

You can then run `round_up` without parentheses and check the `namespace` signature at the bottom. If it says `namespace:roundwork`, everything is fine. If not, please [open an issue](https://github.com/lhdjung/roundwork/issues).
