---
title: "Relation to scrutiny"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Relation to scrutiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The roundwork package was outsourced from [scrutiny](https://lhdjung.github.io/scrutiny/), a much larger and less focused package. (See [this Github issue](https://github.com/ianhussey/ERROR/issues/6) for the rationale.)

roundwork holds the rounding layer and nothing else:

-   the individual rounding procedures (`round_up()`, `round_ceiling()`, `round_ties_away()`, ...);
-   `reround()`, the string-driven interface to all of them;
-   `unround()` and `bound_numerators()`, which run the same procedures backwards to recover the range of an original number;
-   `reround_to_fraction()` and `rounding_bias()`.

The error detection techniques that build on this layer --- GRIM, GRIMMER, DEBIT --- live elsewhere.

## Resolving conflicts

The rounding functions are still part of scrutiny under the same names, so attaching both packages can create ambiguity. Use the [conflicted](https://conflicted.r-lib.org/index.html) package to say which one you mean:

```{r eval=FALSE}
library(conflicted)
library(scrutiny)
library(roundwork)
conflict_prefer_matching("round", "roundwork", quiet = TRUE)
```

You can then run `round_up` without parentheses and check the `namespace` signature at the bottom. If it says `namespace:roundwork`, everything is fine. If not, please [open an issue](https://github.com/lhdjung/roundwork/issues).

Package developers should simply use `package::function()` syntax, as usual.
